---
title: "EXAMPLE!"
author: "Josiah King"
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(patchwork)
source('_theme/theme_quarto.R')
```

# Course Overview

```{r}
#| results: "asis"
#| echo: false
block1_name = "multilevel modelling<br>working with group structured data"
block1_lecs = c("regression refresher",
                "introducing multilevel models",
                "more complex groupings",
                "centering, assumptions, and diagnostics",
                "recap")
block2_name = "factor analysis<br>working with multi-item measures"
block2_lecs = c(
  "what is a psychometric test?",
  "using composite scores to simplify data (PCA)",
  "uncovering underlying constructs (EFA)",
  "more EFA",
  "recap & exam prep"
  )

source("https://raw.githubusercontent.com/uoepsy/junk/main/R/course_table.R")

course_table(block1_name,block2_name,block1_lecs,block2_lecs,week=10)
```


# This week {transition="slide"}

- Lec1: Recap of core concepts
- Lec2: Exam prep session
- Lab: Mock Exam Qs

# Broad ideas 

## multivariate



::::{.columns}
:::{.column width="50%"}
__mixed models/multi-level models__  

- multiple values per cluster
- each value is an observation


```{r}
#| echo: false
tibble(
  person = rep(1:3,e=3),
  y = "...",
  x = "...",
  ` ...`= "..."
) |> gt::gt()
```

:::
:::{.column width="50%"}
__pscyhometrics__  

- multiple values ($y1, ..., y_k$) representing the same construct
- the set of values is "an observation" of Y

```{r}
#| echo: false
tibble(
  person = c(1:3,"..."),
  y1 = c("..."),
  y2 = c("..."),
  y3 = c("..."),
  ` ...` = c("..."),
) |> gt::gt()
```

:::
::::

## two questions


:::{.incremental}

- Q: To do anything with [construct Y], how do we get one number to represent an observation of Y?  
    - is one number enough - are $y1,y2,...,yk$ really unidimensional?  
    
<br><br>    
    
- Q: How does [set of scores $y1,y2,...,yk$] get at [construct Y]?  
    - is it a reliable measure?
    - are the variables equally representative?
    - is there just one dimension to Y or are there multiple?


:::



## scoring multi-item measures


::::{.columns}
:::{.column width="50%"}
**scale scores**  
add 'em all up, you've got Y  

- clinically 'meaningful'?  
- but only 'meaningful' if underlying model holds (which it almost definitely doesn't!)  
    
:::

:::{.column width="50%"}
**dimension reduction**  
identify dimensions that capture how people co-vary across across the items

- PCA: reduce to set of orthogonal dimensions sequentially capturing most variability

- FA: develop theoretical model of underlying dimensions (possibly correlated) that explain variability in items  

:::
::::


## understanding multi-item measures

::::{.columns}
:::{.column width="50%"}

:::

:::{.column width="50%"}
**dimension reduction**  

:::{style="opacity:.4"}
identify dimensions that capture how people co-vary across across the items

- PCA: reduce to set of orthogonal dimensions sequentially capturing most variability
    
::: 

- FA: develop theoretical model of underlying dimensions (possibly correlated) that explain variability in items  

:::
::::

## understanding multi-item measures

$$
\begin{align}
\text{Outcome} &=& \text{Model} &\quad + \quad& \text{Error} \\
\quad \\
\text{observed correlation} &=& \text{factor loadings and} &\quad + \quad& \text{unique variance for} \\
\text{matrix of items}& &\text{factor correlations} &\quad + \quad& \text{each item} \\
\end{align}
$$

# section 2


# End!  









